---
title: "Ring Test Plots"
output: html_notebook
---

Libraries
```{r}
library(dplyr)
library(ggplot2)
library(viridis)
library(reshape2)
library(reshape2)
library(dunn.test)

```

Figure 2. Qubit boxplots for UIBK samples
```{r}
uibk <- read.csv("qubit_uibk_jan21.csv")
ggplot(uibk, aes(x = as.factor(Number), y = ng.ul)) +
  geom_boxplot() + # Boxplot for each sample number
  geom_point(aes(color = Org), position = position_jitter(width = 0.2), size = 2.5) + # Points colored by lab, slightly jittered
  theme_minimal() +
  scale_color_manual(values = custom_colors) +
  labs(x = "", 
       y = "",
       color = "Lab") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14), # Increase x-axis text size
        axis.text.y = element_text(size = 14), # Increase y-axis text size
        axis.title.x = element_text(size = 16), # Increase x-axis title size
        axis.title.y = element_text(size = 16), # Increase y-axis title size
        legend.title = element_text(size = 14), # Increase legend title size
        legend.text = element_text(size = 14)) # Increase legend text size

```
Figure 2. Qubit boxplots for INRAE samples
```{r}
inrae <- read.csv("qubit_inrae_jan24.csv")
ggplot(inrae, aes(x = as.factor(Number), y = ng.ul)) +
  geom_boxplot() + # Boxplot for each sample number
  geom_point(aes(color = Org), position = position_jitter(width = 0.2), size = 2.5) + # Points colored by lab, slightly jittered
  theme_minimal() +
  scale_color_manual(values = custom_colors) +
  labs(x = "", 
       y = "",
       color = "Lab") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14), # Increase x-axis text size
        axis.text.y = element_text(size = 14), # Increase y-axis text size
        axis.title.x = element_text(size = 16), # Increase x-axis title size
        axis.title.y = element_text(size = 16), # Increase y-axis title size
        legend.title = element_text(size = 14), # Increase legend title size
        legend.text = element_text(size = 14)) # Increase legend text size

```
Figure 2. Qubit boxplots for UCC samples
```{r}
ucc <- read.csv("qubit_ucc_feb4.csv")
ggplot(ucc, aes(x = as.factor(Number), y = ng.ul)) +
  geom_boxplot() + # Boxplot for each sample number
  geom_point(aes(color = Org), position = position_jitter(width = 0.2), size = 2.5) + # Points colored by lab, slightly jittered
  theme_minimal() +
  scale_color_manual(values = custom_colors) +
  labs(x = "", 
       y = "",
       color = "Lab") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14), # Increase x-axis text size
        axis.text.y = element_text(size = 14), # Increase y-axis text size
        axis.title.x = element_text(size = 16), # Increase x-axis title size
        axis.title.y = element_text(size = 16), # Increase y-axis title size
        legend.title = element_text(size = 14), # Increase legend title size
        legend.text = element_text(size = 14)) # Increase legend text size

```

Figure 2. Qubit boxplots for IMR samples
```{r}
imr <- read.csv("qubit_imr_jan19.csv")
ggplot(imr, aes(x = as.factor(Number), y = ng.ul)) +
  geom_boxplot() + # Boxplot for each sample number
  geom_point(aes(color = Org), position = position_jitter(width = 0.2), size = 2.5) + # Points colored by lab, slightly jittered
  theme_minimal() +
  scale_color_manual(values = custom_colors) +
  labs(x = "", 
       y = "",
       color = "Lab") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14), # Increase x-axis text size
        axis.text.y = element_text(size = 14), # Increase y-axis text size
        axis.title.x = element_text(size = 16), # Increase x-axis title size
        axis.title.y = element_text(size = 16), # Increase y-axis title size
        legend.title = element_text(size = 14), # Increase legend title size
        legend.text = element_text(size = 14)) # Increase legend text size

```
Figure 3. Ct values and Limit of Detection for dilution series and eDNA extracts (UIBK)
```{r}
df <- read.csv("UIBK_data_qpcr.csv")

df$Sample <- factor(df$Sample, levels = c("SW1", "SW2", "SW3", "SW4", "SW5", "SW6", "SW7", "SW8", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11"))

df$Ct <- as.numeric(as.character(df$Ct))

custom_colors <- c("#E69F00", "#56B4E9", "#009E73", "#CC79A7")
ggplot(df, aes(x = Sample, y = Ct, color = Lab, shape = Sample.type)) +
  geom_point(aes(color = Lab), size = 2.5) + # Thick black line at Ct=40
  geom_hline(yintercept = 35.5, linetype = "dotted", color = "blue", size = 1) +
  #geom_hline(yintercept = 31.5, linetype = "dotted", color = "orange4", size = 1) + # Dotted blue line at Ct=32# Dotted blue line at Ct=33 + 
# Dotted blue line at Ct=36 + 
  scale_y_continuous(breaks = seq(20, max(df$Ct, na.rm = TRUE) + 2, by = 2)) + # Adjust y-axis intervals
  scale_x_discrete(limits = levels(df$Sample)) + # Ensure the reordering is applied
  theme_minimal() +
  scale_color_manual(values = custom_colors) +
  labs(x = " ", y = " ",
       color = "Laboratory / 
       Extraction Method", # Custom title for the color legend
       shape = "Type of Sample") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14), # Increase x-axis text size
        axis.text.y = element_text(size = 14), # Increase y-axis text size
        axis.title.x = element_text(size = 16), # Increase x-axis title size
        axis.title.y = element_text(size = 16), # Increase y-axis title size
        legend.title = element_text(size = 14), # Increase legend title size
        legend.text = element_text(size = 14)) # Increase legend text size

```

Figure 3. Ct values and Limit of Detection for dilution series and eDNA extracts (INRAE)
```{r}
df <- read.csv("INRAE_data_qpcr.csv")

df$Sample <- factor(df$Sample, levels = c("P1", "P2", "P3", "P4", "P5", "P6", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21"))

df$Ct <- as.numeric(as.character(df$Ct))
custom_colors <- c("#E69F00", "#56B4E9", "#009E73", "#CC79A7")

ggplot(df, aes(x = Sample, y = Ct, color = Lab, shape = Sample.type)) +
  geom_point(aes(color = Lab), size = 2.5) + # Thick black line at Ct=40
  geom_hline(yintercept = 35.9, linetype = "dotted", color = "blue", size = 1) +
  #geom_hline(yintercept = 31.5, linetype = "dotted", color = "orange4", size = 1) + # Dotted blue line at Ct=32# Dotted blue line at Ct=33 + 
# Dotted blue line at Ct=36 + 
  scale_y_continuous(breaks = seq(20, max(df$Ct, na.rm = TRUE) + 2, by = 2)) + # Adjust y-axis intervals
  scale_x_discrete(limits = levels(df$Sample)) + # Ensure the reordering is applied
  theme_minimal() +
  scale_color_manual(values = custom_colors) +
  labs(x = " ", y = " ",
       color = "Laboratory / 
       Extraction Method", # Custom title for the color legend
       shape = "Type of Sample") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14), # Increase x-axis text size
        axis.text.y = element_text(size = 14), # Increase y-axis text size
        axis.title.x = element_text(size = 16), # Increase x-axis title size
        axis.title.y = element_text(size = 16), # Increase y-axis title size
        legend.title = element_text(size = 14), # Increase legend title size
        legend.text = element_text(size = 14)) # Increase legend text size


```

Figure 3. Ct values and Limit of Detection for dilution series and eDNA extracts (UCC)
```{r}
df <- read.csv("UCC_data_qpcr.csv")

df$Sample <- factor(df$Sample, levels = c("BD1", "BD2", "BD3", "BD4", "BD5", "BD6", "22", "23", "24", "25", "26", "27", "28", "29", "30", "31"))

df$Ct <- as.numeric(as.character(df$Ct))
custom_colors <- c("#E69F00", "#56B4E9", "#009E73", "#CC79A7")

ggplot(df, aes(x = Sample, y = Ct, color = Lab, shape = Sample.type)) +
  geom_point(aes(color = Lab), size = 2.5) + # Thick black line at Ct=40
  geom_hline(yintercept = 36, linetype = "dotted", color = "blue", size = 1) +
  #geom_hline(yintercept = 31.5, linetype = "dotted", color = "orange4", size = 1) + # Dotted blue line at Ct=32# Dotted blue line at Ct=33 + 
# Dotted blue line at Ct=36 + 
  scale_y_continuous(breaks = seq(20, max(df$Ct, na.rm = TRUE) + 2, by = 2)) + # Adjust y-axis intervals
  scale_x_discrete(limits = levels(df$Sample)) + # Ensure the reordering is applied
  theme_minimal() +
  scale_color_manual(values = custom_colors) +
  labs(x = " ", y = " ",
       color = "Laboratory / 
       Extraction Method", # Custom title for the color legend
       shape = "Type of Sample") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14), # Increase x-axis text size
        axis.text.y = element_text(size = 14), # Increase y-axis text size
        axis.title.x = element_text(size = 16), # Increase x-axis title size
        axis.title.y = element_text(size = 16), # Increase y-axis title size
        legend.title = element_text(size = 14), # Increase legend title size
        legend.text = element_text(size = 14)) # Increase legend text size

```

Figure 3. Ct values and Limit of Detection for dilution series and eDNA extracts (IMR)
```{r}

df <- read.csv("IMR_data_qpcr.csv")

df$Sample <- factor(df$Sample, levels = c("B1", "B2", "B3", "B4", "B5", "B6", "32", "33", "34", "35", "36", "37", "38", "39"))

df$Ct <- as.numeric(as.character(df$Ct))
custom_colors <- c("#E69F00", "#56B4E9", "#009E73", "#CC79A7")

ggplot(df, aes(x = Sample, y = Ct, color = Lab, shape = Sample.type)) +
  geom_point(aes(color = Lab), size = 2.5) + 
  geom_hline(yintercept = 35.3, linetype = "dotted", color = "blue", size = 1) +
  scale_y_continuous(breaks = seq(20, max(df$Ct, na.rm = TRUE) + 2, by = 2)) + 
  scale_x_discrete(limits = levels(df$Sample)) + 
  theme_minimal() +
  scale_color_manual(values = custom_colors) +
  labs(x = " ", y = " ",
       color = "Laboratory / 
       Extraction Method", # Custom title for the color legend
       shape = "Type of Sample") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14), # Increase x-axis text size
        axis.text.y = element_text(size = 14), # Increase y-axis text size
        axis.title.x = element_text(size = 16), # Increase x-axis title size
        axis.title.y = element_text(size = 16), # Increase y-axis title size
        legend.title = element_text(size = 14), # Increase legend title size
        legend.text = element_text(size = 14)) # Increase legend text size

```

Figure 4A. qPCR heatmap with all positive amplifications
```{r}
data <- read.csv("heatmap_All_Positive_Amplifications.csv")

data$Replicate <- factor(data$Replicate, levels = c("A", "B", "C"))  
data$LabReplicate <- paste(data$Lab, data$Replicate, sep = "_")
data$Unique <- as.numeric(data$Unique)
data <- data %>% mutate(CtAdjusted = ifelse(Ct == 0, NA, Ct))
data <- data %>%
  group_by(Lab) %>%
  mutate(LabPosition = mean(as.numeric(factor(LabReplicate)))) %>%
  ungroup()

data$LabReplicate <- factor(data$LabReplicate, levels = c("UIBK_A", "UIBK_B", "UIBK_C", "INRAE_A", "INRAE_B", "INRAE_C", "UCC_A", "UCC_B", "UCC_C", "IMR_A", "IMR_B", "IMR_C"))

ggplot(data, aes(x = LabReplicate, y = Unique, fill = CtAdjusted)) + 
  geom_tile(color = "grey", linewidth = 0.2) +
  scale_fill_gradientn(colors = c("white", "darkblue", "lightblue"),
                       values = rescale(c(NA, 10, max(data$Ct, na.rm = TRUE))), 
                       na.value = "white", 
                       guide = "colourbar") +
  theme_minimal() +
  labs(fill = "Ct", 
       x = "", 
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to =40, by = 5)) + 
  scale_x_discrete(limits = levels(data$LabReplicate))

```
Figure 4B. qPCR heatmap with positive amplifications at or below the respective assay's LOD
```{r}
data <- read.csv("lod-ct.csv")
data$Replicate <- factor(data$Replicate, levels = c("A", "B", "C"))  
data$LabReplicate <- paste(data$Lab, data$Replicate, sep = "_")
data$Unique <- as.numeric(data$Unique)
data <- data %>% mutate(CtAdjusted = ifelse(Ct == 0, NA, Ct))

data <- data %>%
  group_by(Lab) %>%
  mutate(LabPosition = mean(as.numeric(factor(LabReplicate)))) %>%
  ungroup()


data$LabReplicate <- factor(data$LabReplicate, levels = c("UIBK_A", "UIBK_B", "UIBK_C", "INRAE_A", "INRAE_B", "INRAE_C", "UCC_A", "UCC_B", "UCC_C", "IMR_A", "IMR_B", "IMR_C"))

ggplot(data, aes(x = LabReplicate, y = Unique, fill = CtAdjusted)) + 
  geom_tile(color = "grey", linewidth = 0.2) +
  scale_fill_gradientn(colors = c("white", "darkblue", "lightblue"),
                       values = rescale(c(NA, 10, max(data$Ct, na.rm = TRUE))), 
                       na.value = "white", 
                       guide = "colourbar") +
  theme_minimal() +
  labs(fill = "Ct", 
       x = "", 
       y = "") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(breaks = seq(from = 0, to =40, by = 5)) + 
  scale_x_discrete(limits = levels(data$LabReplicate))

```
Supplementary Figure 1
```{r}
ggplot(uibk, aes(x = as.factor(Number), y = ng.ul)) + 
  geom_boxplot(aes(fill = Org), outlier.shape = NA) + 
  geom_jitter(position = position_jitter(width = 0.2), size = 1) +
  labs(x = "Sample", y = "DNA Concentration") +
  scale_fill_manual(values = c("UIBK" = "#cc79a7", "UCC" = "#009e73", "INRAE" = "#e69f00", "IMR" = "#0072b2")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  facet_grid(rows = vars(Org), scales = "free", space = "free") +
  theme(strip.background = element_blank(), strip.text.y = element_text(size = 12, face = "bold")) + ylim(0, 6)
```

Supplementary Figure 1
```{r}
ggplot(inrae, aes(x = as.factor(Number), y = ng.ul)) + 
  geom_boxplot(aes(fill = Org), outlier.shape = NA) + 
  geom_jitter(position = position_jitter(width = 0.2), size = 1) +
  labs(x = "Sample", y = "DNA Concentration") +
  scale_fill_manual(values = c("UIBK" = "#cc79a7", "UCC" = "#009e73", "INRAE" = "#e69f00", "IMR" = "#0072b2")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  facet_grid(rows = vars(Org), scales = "free", space = "free") +
  theme(strip.background = element_blank(), strip.text.y = element_text(size = 12, face = "bold")) + ylim(0, 6)
```
Supplementary Figure 1
```{r}
ggplot(ucc, aes(x = as.factor(Number), y = ng.ul)) + 
  geom_boxplot(aes(fill = Org), outlier.shape = NA) + 
  geom_jitter(position = position_jitter(width = 0.2), size = 1) +
  labs(x = "Sample", y = "DNA Concentration") +
  scale_fill_manual(values = c("UIBK" = "#cc79a7", "UCC" = "#009e73", "INRAE" = "#e69f00", "IMR" = "#0072b2")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  facet_grid(rows = vars(Org), scales = "free", space = "free") +
  theme(strip.background = element_blank(), strip.text.y = element_text(size = 12, face = "bold")) + ylim(0, 6)
```
Supplementary Figure 1
```{r}
ggplot(imr, aes(x = as.factor(Number), y = ng.ul)) + 
  geom_boxplot(aes(fill = Org), outlier.shape = NA) + 
  geom_jitter(position = position_jitter(width = 0.2), size = 1) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +  
  labs(x = "Sample", y = "DNA Concentration") +
  scale_fill_manual(values = c("UIBK" = "#cc79a7", "UCC" = "#009e73", "INRAE" = "#e69f00", "IMR" = "#0072b2")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  facet_grid(rows = vars(Org), scales = "free", space = "free") +
  theme(strip.background = element_blank(), strip.text.y = element_text(size = 12, face = "bold")) + 
  ylim(0, 18)
```

Supplementary Figure 2A
```{r}
custom_palette <- c("skyblue", "orange", "darkgreen", "#B63679FF", "grey50")

ggplot(data = data, aes(x = Target, y = Ct)) +
  geom_boxplot(data = subset(data, Ct != 0), outlier.shape = NA, color = "black") +
  geom_jitter(aes(color = Lab), width = 0.2) +
  theme_minimal() +
  labs(title = "", x = "", y = "") +
  theme(legend.position = "right",
        axis.title = element_text(size = 20),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 10)) +
  scale_color_manual(values = custom_palette) 

```

Supplementary Figure 2B
```{r}
d <- read.csv("lod-ct.csv")
ggplot(data = d, aes(x = Target, y = Ct)) +
  geom_boxplot(data = subset(d, Ct != 0), outlier.shape = NA) +
  geom_jitter(aes(color = Lab), width = 0.2) +
  theme_minimal() +
  labs(title = "", x = "", y = "") +
  theme(legend.position = "right",
        axis.title = element_text(size = 20),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14),
        axis.text = element_text(size = 10)) +
  scale_color_manual(values = custom_palette) 

```
Statistical Analysis(All data)
```{r}
a <- read.csv("heatmap_All_Positive_Amplifications.csv")

atable <- table(a$Lab, a$Detect)
atable
chisq.test(atable)
std_residuals <- chisq.test(atable)$stdres
residual_table <- as.data.frame(std_residuals)
names(residual_table) <- c("Residuals")
rownames(residual_table) <- apply(expand.grid(rownames(table), colnames(table)), 1, paste, collapse = " in ")

# Print residuals to identify significant deviations
print(residual_table)
```

```{r}
chi_sq_value <- chisq.test(table)$statistic
N <- sum(table)
for (i in 1:(nrow(table) - 1)) {
  for (j in (i + 1):nrow(table)) {
    prop_diff <- abs(prop.table(table)[i, 2] - prop.table(table)[j, 2])
    crit_value <- sqrt((chi_sq_value / N) * (1 / sum(table[i, ]) + 1 / sum(table[j, ])))
    print(c(paste("Comparison between", rownames(table)[i], "and", rownames(table)[j]), prop_diff > crit_value))
  }
}
```

```{r}
all <- read.csv("heatmap_All_Positive_Amplifications.csv")

data_posive <- subset(all, Detect == "Y")

shapiro.test(data_positive$Ct)
hist(data_positive$Ct, main = "Histogram of Ct Values", xlab = "Ct", breaks = 30, col = "blue")

# Q-Q Plot
qqnorm(data_positive$Ct)
qqline(data_positive$Ct, col = "red")
library(car)
leveneTest(Ct ~ Lab, data = data_positive)

results <- data_positive %>%
  group_by(Target) %>%
  do({
    anova_result <- aov(Ct ~ Lab, data = .)
    summary_df <- summary(anova_result)
    p_value <- summary_df[[1]][["Pr(>F)"]][1]
    data.frame(
      Target = unique(.$Target),
      P_Value = p_value,
      Summary = I(list(summary_df))
    )
  })

# View the results
print(results)
install.packages("multcomp")

library(multcomp)
tukey_res <- glht(anova_result, linfct = mcp(Lab = "Tukey"))
summary(tukey_res)

kruskal_test_result <- kruskal.test(Ct ~ Lab, data = data_positive)
print(kruskal_test_result)

anova_result <- aov(Ct ~ Lab, data = data_positive)
print(anova_result)

library(dunn.test)

# Dunn's Test for multiple comparisons
dunn_result <- dunn.test(data_positive$Ct, data_positive$Lab, method = "bonferroni")
print(dunn_result)

dunn_data <- data.frame(
  Comparison = rownames(dunn_result$comparisons),
  Z_value = dunn_result$comparisons[, ""],
  P_value = dunn_result$comparisons[, "P"],
  Adjusted_P_value = dunn_result$comparisons[, "P.adjusted"]
)
```

Statistical Analysis (At or Below assay LOD)
```{r}
lod <- read.csv("lod-ct.csv")

data_pos_lod <- subset(lod, Detect == "Y")

shapiro.test(data_pos_lod$Ct)
hist(data_pos_lod$Ct, main = "Histogram of Ct Values", xlab = "Ct", breaks = 30, col = "blue")

# Q-Q Plot
qqnorm(data_positive$Ct)
qqline(data_positive$Ct, col = "red")
library(car)
leveneTest(Ct ~ Lab, data = data_positive)

results <- data_positive %>%
  group_by(Target) %>%
  do({
    anova_result <- aov(Ct ~ Lab, data = .)
    summary_df <- summary(anova_result)
    p_value <- summary_df[[1]][["Pr(>F)"]][1]
    data.frame(
      Target = unique(.$Target),
      P_Value = p_value,
      Summary = I(list(summary_df))
    )
  })

# View the results
print(results)
install.packages("multcomp")

library(multcomp)
tukey_res <- glht(anova_result, linfct = mcp(Lab = "Tukey"))
summary(tukey_res)

kruskal_test_result <- kruskal.test(Ct ~ Lab, data = data_pos_lod)
print(kruskal_test_result)

anova_result <- aov(Ct ~ Lab, data = data_pos_lod)
print(anova_result)


# Dunn's Test for multiple comparisons
dunn_result <- dunn.test(data_pos_lod$Ct, data_pos_lod$Lab, method = "bonferroni")
print(dunn_result)

dunn_data <- data.frame(
  Comparison = rownames(dunn_result$comparisons),
  Z_value = dunn_result$comparisons[, ""],
  P_value = dunn_result$comparisons[, "P"],
  Adjusted_P_value = dunn_result$comparisons[, "P.adjusted"]
)
```

